Accessing biological data in R with semantic web technologies

### 2014-03-15 article.tex
Fixed a random insert error

\begin{footnotesize}
\begin{verbatim}
library(biomaRt)
mart = biomaNoy2009Rt::useMart(biomart="snp", dataset="hsapiens_snp")
brca1 = c("rs16940","rs16941", "rs16942", "rs799916", "rs799917")
attribs = c(
  "refsnp_id", "chr_name", "chrom_start",
  "validated", "pmid_20137", "allele"
)
data = biomaRt::getBM(
  attributes=attribs, filters=c("snp_filter"), values=brca1, mart=mart
)
\end{verbatim}
\end{footnotesize}

>>>>

\begin{footnotesize}
\begin{verbatim}
library(biomaRt)
mart = biomaRt::useMart(biomart="snp", dataset="hsapiens_snp")
brca1 = c("rs16940","rs16941", "rs16942", "rs799916", "rs799917")
attribs = c(
  "refsnp_id", "chr_name", "chrom_start",
  "validated", "pmid_20137", "allele"
)
data = biomaRt::getBM(
  attributes=attribs, filters=c("snp_filter"), values=brca1, mart=mart
)
\end{verbatim}
\end{footnotesize}
